Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-02-14 automatica/paper.tex
updated sections of the automatica journal
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}                          % Abstract of not more than 200 words.
\textcolor{red}{Lucas: We have to write a new abstract.}
\end{abstract}

@@

\textcolor{red}{Pascal: can you please describe here the experimental results?}

@@

\textcolor{red}{Pascal: can you please describe here the threats to validity?}

@@

\textcolor{red}{Lucas: We need to write a new conclusions about this work.}

>>>>

\begin{abstract}                          % Abstract of not more than 200 words.
\textcolor{red}{Cristina: Can you please write an initial version of the abstract.}
\end{abstract}

@@

\textcolor{red}{Lucas describe here the experimental results}

@@

\textcolor{red}{Lucas: describe here the threats to validity}

@@

\textcolor{red}{Cristina: Can you please write an initial version of the conclusions?}
